Pass 3 Comparison

### 2025-04-09 studies/search_syntax.qmd
rendered the html versions

Out of the studies identified in the first pass, a closer look at the priority 2 studies using the criteria established [link to prereg] was carried out.

>>>>

Out of the studies identified in the first pass, a closer look at the priority 2 studies using the criteria established in the [preregistration plan](../preregistration/preregistration.qmd) was carried out.
